Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-12-08 paper.tex
A paragraph on other application types, following discussion with @merous

>>>>

\subsection{Application types}

So far, \boutiques has focused on the description of non-interactive
command-line applications. While such applications cover a large
fractions of the tools involved in scientific data processing, other
types of programs exist such as web services, interactive tools, and
applications with a graphical user interface (GUI).  Such application
classes could be described in \boutiques through a command-line
mapping. For instance, web services may be wrapped as command-line
applications using tools such as \texttt{curl} or
\texttt{wget}. Interactive applications may also be transformed to
non-interactive ones through configuration files. Finally, nothing
prevents a \boutiques tool from popping up a window for a user to
provide input through a GUI. This should, however, be specified
as an extension to the manifest since most platforms would not support
this feature by default. Graphical output produced by applications
executed in containers should also be treated specifically.
